---
title: "lobster_abundance_stats"
author: "Gabriel De La Rosa, Dylan Glave"
date: "11/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = FALSE,echo = FALSE, warning = FALSE)
```



```{r}
### Reading in Packages

library(tidyverse)
library(janitor)
library(effsize)
library(here)
library(kableExtra)
library(ggridges)
library(forcats)
```


```{r}
### Reading in Data

lobster_abundance <- read_csv("lobster_abundance_sbc_lter.csv", na = "-99999") %>%
  clean_names() 
```


```{r}
### Expanding longer with "uncount()" function. Row with "45" lobsters, will now be 45 observations. Removed "count" row and gives each counted lobster its own rown

lobster_tidy <- lobster_abundance %>% 
  tidyr::uncount(count)
```





```{r}
#### Each lobster now has its own row. 1 variable per column, 1 observation per row AND 1 measurement per cell. 

#### Adding a new column to show the year and month name of each lobster observation: 


#### Parsed date_new column to get month and year separated. 

lobster_parse_date <- lobster_tidy %>% 
  mutate(obs_month = lubridate::month(date, label = TRUE),
         obs_year = lubridate::year(date)) %>% 
  mutate(site = as.factor(site) %>% 
           forcats::fct_relevel("MOHK", "AQUE", "CARP","NAPL","IVEE"))

view(lobster_parse_date)
```

```{r}
# Yearly counts by site

lob_year <- lobster_abundance %>% 
  mutate(site = as.factor(site) %>% 
           forcats::fct_relevel("MOHK", "AQUE", "CARP","NAPL","IVEE")) %>%
  mutate(mpa =
    site %in% c( "IVEE", "NAPL")) %>% 
  group_by(year, site, mpa) %>%
  count(year)
  

#  Graph these data...

site_graph <-
ggplot(data = lob_year, aes(x = year, y = n, fill = mpa, color = mpa)) +
  geom_line(alpha = 1,
             size = 1) +
  
  
  geom_ribbon(aes(x=year, xend = year, ymin = 0, ymax = n,
             fill = mpa)) +
  
  scale_fill_manual(values = c("firebrick4", "cadetblue4"),
                    labels = c("non-MPA", "MPA")) +
  
  scale_color_manual(values = c("firebrick4", "cadetblue4"),
                     labels = c("non-MPA", "MPA")) +
  
  facet_wrap("site",
             as.table = F) +
  
  scale_y_continuous(expand = c(0,0), limits = c(0, 550)) +
  scale_x_continuous(expand = c(0,0), 
                     breaks = c(2013, 2015, 2017)) +
  
  theme_bw() +
  
  labs(title = "Yearly lobster counts per site", y = "Lobsters counted", x = NULL, fill = "", color = "") +
  
  theme(legend.position = c(0.8, .85),
        legend.title = NULL) +
  
  guides(fill = guide_legend(reverse = TRUE),
         color = guide_legend(reverse = TRUE))


site_graph
```


```{r}
# Results B:

# Pare down data to year, size, site for 2012 and 2018

size_dist <- lobster_parse_date %>% 
  filter(year == c("2018", "2012")) %>%
  select(year, size_mm, site) 

### I didn't end up using this, but keeping it around...

# # Divide data frame by year
#   
# size_2012 <- size_dist %>% 
#   filter(year == "2012")
# 
# size_2018 <- size_dist %>% 
#   filter(year == "2018")
# 
# # Compare size distributions across sites...
# # For 2012
# size_dist_2012 <- ggplot(data = size_2012, aes(x = size_mm)) +
#   geom_histogram() +
#   facet_wrap(c("site"))
# 
# size_dist_2012
# 
# # For 2018
# 
# size_dist_2018 <- ggplot(data = size_2018, aes(x = size_mm)) +
#   geom_histogram() +
#   facet_wrap(c("site"))
# 
# size_dist_2018


# And create mean summary statistics for each group, arrange facets so NAPL and IV are next to each other in the graph, add MPA column

site_mean_mm <- size_dist %>% 
  mutate(site = as.factor(site) %>% 
           forcats::fct_relevel("MOHK", "AQUE", "CARP","NAPL","IVEE")) %>% 
  group_by(site, year) %>% 
  mutate(mean = 
           mean(size_mm)) %>% 
  mutate(mpa =
    site %in% c( "IVEE", "NAPL"))
  
# Ridgeline plot...


year_compare_graph <- 
  ggplot(data = site_mean_mm, 
         aes(x = size_mm,
             y = as.factor(year))) +
    
  geom_rect(data = subset(site_mean_mm,
                          site == "NAPL")[1,],
            aes(fill = "MPA"),
            xmin = -Inf,
            xmax = Inf,
            ymin = -Inf,
            ymax = Inf,
            alpha = 0.4) +

  geom_rect(data = subset(site_mean_mm,
                          site == "IVEE")[1,],
            aes(fill = "MPA"),
            xmin = -Inf,
            xmax = Inf,
            ymin = -Inf,
            ymax = Inf,
            alpha = 0.4) +
  
  geom_density_ridges2(alpha = .9,
                      quantile_lines = TRUE,
                      quantiles = 2,
                      color = "white",
                      aes(fill = as.factor(year)
                          )
                      ) +
    
  scale_fill_manual(values = c("firebrick4", "cadetblue4", "cadetblue3"),
                    breaks = c("2012", "2018")) +
  
  scale_y_discrete(expand = c(0,0)) +
  
  scale_x_continuous(expand = c(0,0), limits = c(25, 125)) +
  
  facet_wrap("site",
             ncol = 3,
             as.table = F,
             ) +
  
  theme_bw() +
    
  theme(legend.position = c(0.75, .85),
        strip.background =element_rect(fill = NA)) +
  
  labs(y = NULL, x = "Size (mm)", title = "Lobster size distribution between 2012 and 2018", fill = "Year")
  
  
year_compare_graph

```




## Introduction





## Data and Methods

Data for this report were collected and provided by the [Santa Barbara Coastal Long Term Environmental Research](https://portal.edirepository.org/nis/metadataviewer?packageid=knb-lter-sbc.77.3) site. 
  Lobster surveys were conducted at five different sites along the mainland side of the Santa Barbara Channel: Naples, Isla Vista, Arroyo Quemado, Mowhawk, and Carpenteria. Naples and Isla Vista are contained within a Marine Protected Area; Arroyo Quemado, Mohawk, and Carpenteria are not. Divers performed four 60m x 5m transects at each site, sampling every two to four weeks through the lobster fishing season (October to March). 

Size is a visual estimate of carapace length in mm. 


## Results

1. 

Lobster counts were compared between sites, and between MPA (Naples Reef, Isla Vista) and non-MPA (Mohawk, Arroyo Quemado, Carpenteria) sites. Both MPA sites saw more lobsters in 2018 than in 2012, with the Isla Vista site showing the strongest response (47 lobsters in 2012, 526 lobsters in 2018). Changes is lobster counts in Non-MPA sites varied greatly: Arroyo Quemado remained relatively stable (53 in 2012, 62 in 2018), Mohawk saw counts double (58 in 2012, 101 in 2018), and Carpenteria saw a strong increase in counted lobster (81 in 2012, 248 in 2018). 



```{r, include= TRUE}
site_graph
```


2. 



```{r ,include = TRUE}
year_compare_graph
```


```{r}

```



Part C 


```{r}
#Created MPA, non MPA df

# Make MPA and non MPA dataframes

lobster_mpa_2012 <- lobster_parse_date %>% 
  mutate(mpa =
    site %in% c( "IVEE", "NAPL")) %>% 
  filter(mpa == "TRUE") %>% 
  filter(year == 2012)

lobster_mpa_2018 <- lobster_parse_date %>% 
  mutate(mpa =
    site %in% c( "IVEE", "NAPL")) %>% 
  filter(mpa %in% "TRUE") %>% 
  filter(year %in% 2018)

lobster_non_2012 <- lobster_parse_date %>% 
  filter(site %in% c("AQUE", "CARP", "MOHK")) %>% 
  filter(year %in% 2012)

lobster_non_2018 <- lobster_parse_date %>% 
  filter(site %in% c("AQUE", "CARP", "MOHK")) %>% 
  filter(year %in% 2018)


# Let's take a look at these data visually first...


ggplot(data = lobster_mpa_2012, aes(x = size_mm)) +
  geom_histogram()

ggplot(data = lobster_mpa_2018, aes(x = size_mm)) +
  geom_histogram()

ggplot(data = lobster_non_2012, aes(x = size_mm)) +
  geom_histogram()

ggplot(data = lobster_non_2018, aes(x = size_mm)) +
  geom_histogram()

# See if theres a difference in means between MPA and non-MPA sites in 2012

t_2012 <- t.test(lobster_mpa_2012$size_mm, lobster_non_2012$size_mm)

t_2012

# Now look for 2018...

t_2018 <- t.test(lobster_mpa_2018$size_mm, lobster_non_2018$size_mm)

t_2018

# Then for MPA sites...

t_mpa <- t.test(lobster_mpa_2012$size_mm,
                lobster_mpa_2018$size_mm)

t_mpa

# Then for non-mpa sites

t_non <- t.test(lobster_non_2012$size_mm,
                lobster_non_2018$size_mm)

t_non

```

```{r}
## Do we still need this?

#ggplot(data = lobster_mpa, aes(x = year, y = size_mm)) +
#  geom_col()
```

```{r}

# Create a summary df with 

lobster_summary <- lobster_parse_date %>% 
   mutate(mpa =
    site %in% c( "IVEE", "NAPL")) %>%
  filter(year %in% c("2012", "2018")) %>% 
  group_by(year, mpa) %>% 
  summarize(
    mean_size_mm = round(mean(size_mm, na.rm = TRUE), 2),
    standard_deviation = round(sd(size_mm, na.rm = TRUE), 2),
    sample_size = n())

# Create table

lobster_table <- lobster_summary %>%
  kable(col.names = c("Year",
"MPA",
"Mean Lobster size (mm)",
"Standard Deviation",
"Sample Size")) %>%
 kable_styling(bootstrap_options = "striped", 
                full_width = F,
                position = "left")  %>%
  add_header_above(c("Average size of Spiny Lobstersin Santa Barbara" = 5))

lobster_table
```


## Summary 




## References





