---
title: "lobster_abundance_stats"
author: "Gabriel De La Rosa, Dylan Glave"
date: "11/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = FALSE,echo = TRUE, warning = FALSE)
```

### Reading in Packages

```{r}
library(tidyverse)
library(janitor)
library(effsize)
library(here)
library(kableExtra)
```

### Reading in Lobster Abundance Data

```{r}
lobster_abundance <- read_csv("lobster_abundance_sbc_lter.csv", na = "-99999") %>% 
  clean_names() 
```


Can I push this back?

view(lobster_abundance)

### Expanding longer with "uncount()" function. Row with "45" lobsters, will now be 45 observations. Removed "count" row and gives each counted lobster its own rown

```{r}
lobster_tidy <- lobster_abundance %>% 
  tidyr::uncount(count)
```


#### Each lobster now has its own row. 1 variable per column, 1 observation per row AND 1 measurement per cell. 

#### Adding a new column to show the actual date of each lobster observation: 


#### Parsed date_new column to get month and year separated. 

```{r}
lobster_parse_date <- lobster_tidy %>% 
  mutate(obs_month = lubridate::month(date, label = TRUE),
         obs_year = lubridate::year(date))
view(lobster_parse_date)
```

